### 2012-07-31 inst/examples/Reed.Rmd

``` {r  SDP_Mat}
pdfn <- function(P, s){
  # dunif(P, 1 - s, 1 + s)
  dlnorm(P, 0, s)
}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g, pdfn)
````

>>>>

``` {r  SDP_Mat}
pdfn <- function(P, s){
  # dunif(P, 1 - s, 1 + s)
  1 + dlnorm(P, 0, s)
}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g, pdfn)
````
